---
title: "ASauk_Biol612_Homework2"
author: "Alexandra Sauk"
date: '2020-01-20'
output: html_document
---

#Scenario 1

##A) Null and alternative hypotheses

Null hypthosis: There is no difference in the shrimp catches from 2009 and 2010.

Alternative hypothesis: There is a difference in the shrimp catches from 2009 and 2010.


##B) Histogram

```{r}
Shrimp_data=read.csv("ASauk_H2_Scenario1_data.csv")

library("reshape2")
library("ggplot2")



Sdf<-melt(Shrimp_data)
colnames(Sdf)<-c('Site','Year', 'Catch')
print(Sdf)
Year<-Sdf$Year
Catch=Sdf$Catch

ggplot(Sdf, aes(x = Catch, fill=Year)) + geom_histogram(alpha = 0.3, position = 'identity') + labs(x = "Shrimp Catch (tonnes)", y ="Observed Frequency", title = "Fig. 1: Histogram of shrimp catches pre and post oil spill") + scale_color_manual(values=c("#3498DB","#F4D03F")) + scale_fill_manual(values=c("#3498DB","#F4D03F"))

```

```{r}
par(mar=c(8.5,6.5,4.1,3.1), mgp=c(3,1,0))

diff<-Shrimp_data$Y2010 - Shrimp_data$Y2009
diff
hist(diff, xlab = "Difference in Shrimp Catch (tonnes)", ylab = "Observed Frequency", col = c("red"), main = NULL, ylim = c(5,0))
title(sub = "Fig. 3: Histogram of Change in Shrimp catches between 2009 and 2010", line=6, cex.sub=1.2)
```


##C) Hypothesis test

The data consists of shrimp catch values from 2009 and 2010 collected from the same villages such that the data is paired. A paired t-test should be used to compare the mean shrimp catches between the two years. 

##D) Hypothesis test results

```{r}
t.test(Shrimp_data$Y2009, Shrimp_data$Y2010, paired = TRUE)
qt(0.975,13)

```


##E) Test statistic

The critical t-value for the paired t-test for this data is 2.16 and the observed t-test value is 6.38. 

##F) Conclusion

In conclusion, the observed t-value is greater than the critical t-value and p<0.05 so we reject the null hypothesis. Thus, there is a statistically significant difference between the mean shrimp catch in 2009 and in 2010 such that there was a significant decrease in the shrimp catches after the oil spill.

#Scenario 2

##A) Null and alternative hypotheses

Null hypthosis: Phosphorous levels in Lake Erie are not different from the guideline level of 15 µg/L. 

Alternative hypothesis: Phosphorous levels in Lake Erie are different from the guideline level of 15 µg/L. 


##B) Histogram

```{r}
Phosphorous_data=read.csv("ASauk_H2_Scenario2_data.csv")
par(mar=c(8.5,6.5,4.1,2.1), mgp=c(3,1,0))
hist(Phosphorous_data$Total.phosphorous, xlab = "Measured level of phosphorous (µg/L)", ylab = "Observed Frequency", col = c("light green"), main = NULL) 
title(sub = "Fig. 4: Histogram of phosphorous levels in Lake Erie", line=6, cex.sub=1.2)
```


##C) Hypothesis test

The appropriate hypothesis test for this data is a one sample t-test as we are comparing observed data to a known value.


##D) Hypothesis test results

```{r}
t.test(Phosphorous_data$Total.phosphorous, mu=15)
qt(0.975,9)
```


##E) Test statistic

The critical t-value for the one sample t-test for this data is 2.26 and the observed t-test value is 1.85.

##F) Conclusion

In conclusion, the observed t-value is less than the critical t-value and p>0.05 so we cannot reject the null hypothesis. Thus, there is no statistically significant difference between the mean phosphorous level in Lake Erie and the guideline level of phosphorous.

#Scenario 3

##A) Null and alternative hypotheses

Null hypthosis: The two diets, carnivrous and vegetaarian, do not differ in terms of growth rate for the farmed salmon.

Alternative hypothesis: The two diets, carnivrous and vegetaarian, do differ in terms of growth rate for the farmed salmon.


##B) Histogram

```{r}
library("reshape2")
library("ggplot2")

Carnivorous<-c(2.3,1.8,1.9,1.8,2.1,2.3,2,2.2,2.2,1.5,1.8,2.1,2.3,2.2,2.3)
Vegetarian<-c(1.6,1.1,0.7,1,1,0.8,1.2,0.8,0.9,0.6,0.7,0.6,0.8,0.8,1.1)
y_name<-'Growth.rate'
x_name<-'Diet'

df<-melt(data.frame(Carnivorous, Vegetarian))
colnames(df)<-c(x_name, y_name)
print(df)
Diet<-df$Diet
Growth.rate=df$Growth.rate
par(mar=c(8.5,6.5,4.1,4.1), mgp=c(3,1,0))
ggplot(df, aes(Growth.rate, fill = Diet)) + geom_histogram(alpha = 0.5) + labs(x = "Growth rate of farmed salmon", y ="Observed Frequency", title = "Fig. 5: Histogram of growth rates of farmed salmon fed \n carnivorous and vegetarian diets")

```


##C) Hypothesis test

The appropriate hypothesis test for this data is a two sample t-test as we are comparing two independent groups.

##D) Hypothesis test results

```{r}
t.test(Carnivorous, Vegetarian)
qt(0.975,27.834)
```


##E) Test statistic

The critical t-value for the one sample t-test for this data is 2.04 and the observed t-test value is 12.264.

##F) Conclusion

In conclusion, the observed t-value is greater than the critical t-value and p<0.05 so we reject the null hypothesis. Thus, there is a statistically significant difference between the growth rates of farmed salmon fed carnivorous and those fed vegetarian diets.

#Scenario 4

##A) Null and alternative hypotheses

Null hypthosis: There is no difference in PCB poisoning between trophic levels. 

Alternative hypothesis: There is a difference in PCB poisoning between trophic levels. 


##B) Histogram

```{r}
PCB_data=read.csv("ASauk_Homework2_Scenario4_data2.csv")


library("ggplot2")

Effect<-PCB_data$Effect


ggplot(PCB_data, aes(x=PCB_data$Trophic.level, y=PCB_data$Individuals, fill = Effect))+geom_bar(stat="identity", position = position_dodge()) + labs(x = "Trophic Level", y = "Number of Individuals", title = "Fig. 6: Effects of PCBs on different trophic levels")

```


##C) Hypothesis test

The appropriate hypothesis test for this data is a chi-squared test. 

##D) Hypothesis test results

```{r}

First<-c(133,100,17)
Top<-c(4,61,35)

dat=data.frame('First'=First, 'Top'=Top)

chisq.test(dat)

qchisq(0.95,2)

```


##E) Test statistic

The critical chi-squared value for the one sample t-test for this data is 5.99 and the observed chi-squared value is 89.253.

##F) Conclusion

In conclusion, the observed chi-squared value is greater than the critical chi-squared and p<0.05 so we reject the null hypothesis. Thus, there is a statistically significant difference between the effects of PCBs on first trophic level organisms and top predators. 