---
title: "ASauk_Biol612_Homework2"
author: "Alexandra Sauk"
date: '2020-01-20'
output: html_document
---

#Scenario 1

##A) Null and alternative hypotheses

Null hypthosis:There is no difference in the shrimp catches from 2009 and 2010.

Alternative hypothesis:There is a difference in the shrimp catches from 2009 and 2010.


##B) Histogram

```{r}
Shrimp_data=read.csv("ASauk_H2_Scenario1_data.csv")
par(mar=c(8.5,6.5,4.1,2.1), mgp=c(3,1,0))
hist(Shrimp_data$X2009.catch, xlab = "Shrimp Catch (tonnes)", ylab = "Observed Frequency", col = c("light blue"), main = NULL, ylim = c(0,4)) 
title(sub = "Fig. 1: Histogram of Shrimp catches in 2009", line=6, cex.sub=1.2)

```
```{r}
par(mar=c(8.5,6.5,4.1,2.1), mgp=c(3,1,0))
hist(Shrimp_data$X2010.catch, xlab = "Shrimp Catch (tonnes)", ylab = "Observed Frequency", col = c("orange"), main = NULL, ylim = c(0,4)) 
title(sub = "Fig. 2: Histogram of Shrimp catches in 2010", line=6, cex.sub=1.2)
```

```{r}
par(mar=c(8.5,6.5,4.1,2.1), mgp=c(3,1,0))
hist(Shrimp_data$X2010.catch - Shrimp_data$X2009.catch, xlab = "Difference in Shrimp Catch (tonnes)", ylab = "Observed Frequency", col = c("red"), main = NULL, ylim = c(4,0))
title(sub = "Fig. 3: Histogram of Change in Shrimp catches between 2009 and 2010", line=6, cex.sub=1.2)
```


##C) Hypothesis test

The data consists of shrimp catch values from 2009 and 2010 collected from the same villages such that the data is paired. A paired t-test should be used to compare the mean shrimp catches between the two years. 

##D) Hypothesis test results

```{r}
t.test(Shrimp_data$X2009.catch, Shrimp_data$X2010.catch, paired = TRUE)
qt(0.95,13)

```


##E) Test statistic

The critical t-value for the paired t-test for this data is 1.77 and the observed t-test value is 6.38. 

##F) Conclusion

In conclusion, the observed t-value is greater than the critical t-value and p<0.05. Thus, there is a statistically significant difference between the mean shrimp catch in 2009 and in 2010 such that there was a significant decrease in the shrimp catches after the oil spill.

#Scenario 2

##A) Null and alternative hypotheses

Null hypthosis:

Alternative hypothesis:


##B) Histogram

##C) Hypothesis test

##D) Hypothesis test results

##E) Test statistic

##F) Conclusion

#Scenario 3

##A) Null and alternative hypotheses

Null hypthosis:

Alternative hypothesis:


##B) Histogram

##C) Hypothesis test

##D) Hypothesis test results

##E) Test statistic

##F) Conclusion

#Scenario 4

##A) Null and alternative hypotheses

Null hypthosis:

Alternative hypothesis:


##B) Histogram

##C) Hypothesis test

##D) Hypothesis test results

##E) Test statistic

##F) Conclusion